Morphological diversity in tenrecs (Afrosoricida, Tenrecidae): Comparing tenrec skull diversity to their closest relatives

### 2015-03-28 paper/PeerJ_resubmission/Supplemental_S1.tex
Figure and supplemental edits after PeerJ request

	\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.8\linewidth, height=0.8\textheight, keepaspectratio]{figures/Gmole_combined_col_light.png}
	\caption[]
		{Landmarks (numbered points) and curves (outlines) for the skulls in dorsal,ventral and lateral view. See Tables S1, S2 and S3 for more detailed landmark descriptions. The skulls are an example of a \textit{Chlorotalpa duthieae} (Duthie's golden mole), museum accession number AMNH 161527.}
	\label{fig:gmole}
	\end{figure}

>>>>

	\begin{figure}[!htbp]
	\centering
	\includegraphics[width=0.8\linewidth, height=0.8\textheight, keepaspectratio]{figures/Gmole_combined_col_light_labels.png}
	\caption[]
		{Landmarks (numbered points) and curves (outlines) for the skulls in dorsal (A), ventral (B) and lateral (C) view. See Tables S1, S2 and S3 for more detailed landmark descriptions. The skulls are an example of a \textit{Chlorotalpa duthieae} (Duthie's golden mole), museum accession number AMNH 161527.}
	\label{fig:gmole}
	\end{figure}
